The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-12-14 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Changes in Future Directions of FT paper

One natural direction of development would be to  incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.

At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.  It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.  For instance, the polynomial $f = x^6+x^2 y^2 + y^3$ is homogeneous under the grading $\deg x = 1, \deg y = 2$, and it is shown that the $F$-threshold of $f$ with respect to the ideal $\langle x, y^2 \rangle$ can be computed as the $F$-pure threshold of $x^3 + x^2 y + y^2$, which is homogeneous under the standard grading.
The package could be improved by finalizing and implementing such an algorithm in greater generality.

Finally, it would be desirable to develop and implement additional algorithms for computing $F$-pure thresholds and $F$-jumping numbers for additional classes of polynomials.  The first, third, and fourth authors, along with Josep \'Alvarez Montaner, Jack Jeffries, and Luis N\'u\~nez-Betancourt,  are currently working on developing such algorithms.  The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, making them natural candidates for  implementation in \emph{Macaulay2}.

>>>>

As a natural and simple way to extend the functionality of the \emph{FrobeniusThresholds} package, we wish to implement a method analogous to \texttt{fpt} to compute $F$-thresholds of polynomials with respect to arbitrary ideals.
Although most of our current specialized algorithms do no extend to such generality, our ``guess-and-check'' methods do, and will likely give us an effective tool in computing or estimating $F$-thresholds.

The lack of specialized algorithms for the computation of $F$-thresholds, noted above, has one exception: the algorithm for computing the $F$-pure threshold of a homogeneous polynomial in two variables.
Results of \cite{HernandezTeixeiraFThresholdFunctions} show that this algorithm can be easily modified to compute $F$-thresholds of such polynomials with respect to ideals generated by two relatively prime homogeneous polynomials.
Once this is implemented, we will be able to compute $F$-thresholds of polynomials in two variables homogeneous under non-standard grading, as those agree with $F$-thresholds of standard-homogeneous polynomials (with respect to different ideals).
For instance, the $F$-pure threshold of the polynomial $x^6+x^2 y^2 + y^3$, homogeneous under the grading $\deg x = 1, \deg y = 2$, can be computed as the $F$-threshold of the standard-homogeneous polynomial $x^6 + x^2 y^4 + y^6$ with respect to the ideal $\langle x, y^2\rangle$.
%The package could be improved by finalizing and implementing such an algorithm in greater generality.

It would be desirable to develop and implement additional algorithms for computing $F$-pure thresholds and $F$-jumping numbers for additional classes of polynomials.
The first, third, and fourth authors, along with Josep \'Alvarez Montaner, Jack Jeffries, and Luis N\'u\~nez-Betancourt,  are currently working on developing such algorithms.
The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, making them natural candidates for  implementation in \emph{Macaulay2}.

Finally, one natural direction of development would be to  incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
